The value of intermediation

### 2022-09-13 src/presentation/presentation.qmd
Add application section to presentation

@@

@@

>>>>

 - Measure 1 of consumers [à la @anderson2021hybrid]
   - Each of them buy a unit of products
   - Logit-type utility function ($u_i = v_i - p_i + \mu \epsilon_i$)
 - Continuum of firms ($a(t), t \in \mathbb{R}$) with one differentiated product each
 - Measure 1 of outside options
 - A platform
   - necessary for the firms to sell their products
   - May or may not have its own products

::: {.notes}
 - Each consumer chooses the products giving them the highest net utility
 - I don't want to go into the details of the model
:::

@@

::: {.column width="45%"}
 1. Firms decide whether to invest at cost $c$
 2. Platform entry fees and decisions are negotiated
 3. Firms and platforms set product prices
 4. Consumers choose products

**Idea:** 2. stage bargaining is over *final allocations*
:::

::: {.notes}
 - Investment decisions are sunk costs
 - Entry fees are lump sum, do not influence pricing
 - All players foresee the outcome of the pricing subgame
:::

@@

 - Assuming no collusion in the pricing game, total profits as a function of entering firms are
$$
v(N_f) = \frac{N_P B + N_F B}{N_P B + N_F B + 1} \quad \text{ where } B = e^\frac{v - c - \mu}{\mu}
$$
 - If entry fees were fixed, $N_P$ would not influence product variety / consumer welfare
 - However, a higher $N_P$ leads to a better bargaining position for the platform and lower number of entrants

::: {.notes}
 - Constant, additive markup over marginal cost
 - Consumer welfare is a function of product variety
:::

## Results graphically
